A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Cite

We initially assume that graphs are unlabelled, undirected and without loops
(\cref{sec:extensions} describes how these restrictions may be relaxed).
The vertices and edge sets of a graph $\graphG$ are denoted $\V(\graphG)$ and $\E(\graphG)$.  The
set of vertices adjacent to vertex $v$ in graph $\graphG$ is called the
\emph{neighbourhood} of $v$, denoted $\N(\graphG, v)$. We denote by $\invN(\graphG, v)$ the
\emph{inverse neighbourhood} of $v$, being the set of the vertices not adjacent
to $v$ (excluding $v$ itself). A \emph{subgraph} of a graph $\graphG$ is a graph
consisting of some of the vertices of $\graphG$, and all of the edges between these
vertices. A \emph{common subgraph} of two graphs is a graph which is
(isomorphic to) a subgraph of two graphs simultaneously, and a \emph{maximum}
common subgraph is one with as many vertices as possible. (In this paper, all
subgraphs are induced. The \emph{maximum common partial subgraph} problem
instead asks for a common non-induced subgraph with as many \emph{edges} as
possible.)

>>>>

We initially assume that graphs are unlabelled, undirected and without loops
(\cref{sec:extensions} describes how these restrictions may be relaxed).
The vertices and edge sets of a graph $\graphG$ are denoted $\V(\graphG)$ and $\E(\graphG)$.  The
set of vertices adjacent to vertex $v$ in graph $\graphG$ is called the
\emph{neighbourhood} of $v$, denoted $\N(\graphG, v)$. We denote by $\invN(\graphG, v)$ the
\emph{inverse neighbourhood} of $v$, being the set of the vertices not adjacent
to $v$ (excluding $v$ itself). A \emph{subgraph} of a graph $\graphG$ is a graph
consisting of some of the vertices of $\graphG$, and all of the edges between these
vertices. A \emph{common subgraph} of two graphs is a graph which is
(isomorphic to) a subgraph of two graphs simultaneously, and a \emph{maximum}
common subgraph is one with as many vertices as possible. (In this paper, all
subgraphs are induced. The \emph{maximum common partial subgraph} problem
instead asks for a common non-induced subgraph with as many \emph{edges} as
possible \citep{DBLP:conf/cp/NdiayeS11}.)
